Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-01-27 reports/manuscript/supplemental.tex
Add missing preprocessing steps to supplemental.tex and corresponding bib items to paper.bib

\todo{Ariel: This section seems incomplete. I am pretty sure there was some motion correction, eddy current correction and so forth happening in here.
Also, we might want to drop the part that describes calculation of confounds,
since we aren't using them.}

Several confounding time-series were calculated based on the
\emph{preprocessed DWI}: framewise displacement (FD) using the
implementation in \emph{Nipype} following the definitions
by \cite{power_fd_dvars}. The head-motion estimates calculated in the
correction step were also placed within the corresponding confounds
file. Slicewise cross correlation was also calculated. The DWI
time-series were resampled to ACPC, generating a \emph{preprocessed DWI
run in ACPC space}.
\end{itemize}

>>>>

Any images with a b-value less than 100 s/mm\^{}2 were treated as a
\emph{b}=0 image. MP-PCA denoising as implemented in MRtrix3's
\texttt{dwidenoise}\cite{dwidenoise1} was applied with a 5-voxel
window. After MP-PCA, B1 field inhomogeneity was corrected using
\texttt{dwibiascorrect} from MRtrix3 with the N4 algorithm \cite{n4}.
After B1 bias correction, the mean intensity of the DWI series was
adjusted so all the mean intensity of the b=0 images matched across
eachseparate DWI scanning sequence.
\end{itemize}

FSL (version 6.0.3:b862cdd5)'s eddy was used for head motion correction
and Eddy current correction \cite{anderssoneddy}. Eddy was configured
with a \(q\)-space smoothing factor of 10, a total of 5 iterations, and
1000 voxels used to estimate hyperparameters. A linear first level model
and a linear second level model were used to characterize Eddy
current-related spatial distortion. \(q\)-space coordinates were
forcefully assigned to shells. Field offset was attempted to be
separated from subject movement. Shells were aligned post-eddy. Eddy's
outlier replacement was run \cite{eddyrepol}. Data were grouped by
slice, only including values from slices determined to contain at least
250 intracerebral voxels. Groups deviating by more than 4 standard
deviations from the prediction had their data replaced with imputed
values. Data was collected with reversed phase-encode blips, resulting
in pairs of images with distortions going in opposite directions. Here,
b=0 reference images with reversed phase encoding directions were used
along with an equal number of b=0 images extracted from the DWI scans.
From these pairs the susceptibility-induced off-resonance field was
estimated using a method similar to that described in \cite{topup}. The
fieldmaps were ultimately incorporated into the Eddy current and head
motion correction interpolation. Final interpolation was performed using
the \texttt{jac} method.

Several confounding time-series were calculated based on the
\emph{preprocessed DWI}: framewise displacement (FD) using the implementation
in \emph{Nipype} following the definitions by \cite{power_fd_dvars}. The DWI
time-series were resampled to ACPC, generating a \emph{preprocessed DWI run
in ACPC space}.
